% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@sudo.ws> http://www.sudo.ws/todd
% (c) 2018 Danh DOAN <congdanhqx@gmail.com>
% vim: et ts=2 sw=2
%
% The template is licensed under the Creative Commons Attribution-ShareAlike 3.0
% Unported License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to
% Creative Commons
% 171 Second Street, Suite 300
% San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage{fancyhdr}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\setlength{\headsep}{30pt}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{
  {\large \colorbox{mygrey}
    {\begin{minipage}{\textwidth}
      {\textbf{#1 \vphantom{p\^{E}}}}
    \end{minipage}}}}
\newcommand{\ressubheading}[4]{
		\textbf{#1} \hfill #2 \\
    \textit{#3} \hfill \textit{#4}}
\newcommand{\resproject}[2]{
  \textbf{#1:} \textit{#2}}

\newcommand{\email}[1]{\href{mailto:#1}{#1}}
\def\Plus{\texttt{+}}
\def\Minus{\texttt{-}}
\def\cplusplus{C\Plus\Plus}
%-----------------------------------------------------------
\pagestyle{fancy}
\fancyhead[C]{\textbf{\Large Danh DOAN}}
\fancyfoot[C]{Danh DOAN - Résumé - Page \thepage}

\begin{document}

Ho Chi Minh city \hfill \email{congdanhqx@gmail.com}

Vietnam  \hfill \url{https://danh.dev}

\begin{center}
  \Large Software Engineer
\end{center}

\resheading{Highlights of Qualifications}
\begin{itemize}
  \item Have critical thinking mindset, solved wide range problems
    with different programming languages included but not limited to
    C, C++, sh, etc...
  \item Worked and gained good understanding with different version control
    systems like git(1), svn(1).
\end{itemize}

\resheading{Software Development Experience}
\begin{itemize}
\item \ressubheading{\href{https://www.larion.com/}{Larion}}{Ho Chi Minh city,
    Vietnam}{Software Engineer}{Feb. 2019 - Apr. 2019}
  \begin{itemize}
    \item \resproject{Mars}{Developing module to process data for a financial
      analysis firm}
      \begin{itemize}
        \item Use \cplusplus{} to develop module that processes external
          data into internal formatted data.
      \end{itemize}
  \end{itemize}

\item \ressubheading{\href{https://www.luxoft.com/}{Luxoft Vietnam}}{Ho Chi Minh
    city, Vietnam}{Software Engineer}{Nov. 2015 - Mar. 2017 \& Jan. 2018 - Dec. 2018}
  \begin{itemize}
    \item \resproject{DN8}{Developing HMI model/view for cars built by
      a Korean corporation}
      \begin{itemize}
        \item Worked with OSEK, Embedded C++
        \item Source code was tracked with git
      \end{itemize}
    \item \resproject{MQB}{Maintain \cplusplus{} widget and animation layer
      for cars built by a Germany manufacture}
      \begin{itemize}
        \item Add features into existing widget and animation upon request
        \item Corporate with model/view team to investigate and fix bug
        \item Make shell and groovy scripts for testing tasks.
        \item Worked with OSEK, Embedded C++
        \item Source code was tracked with git
      \end{itemize}
    \item \resproject{DIS2}{Develop HMI system for car built by a Korean
      corporation}
      \begin{itemize}
        \item Ran system integration testing
        \item Fixed minor bugs
        \item Used technology: \cplusplus{}, xml, Perforce p4
      \end{itemize}
  \end{itemize}

\item \ressubheading{\href{http://www.informa.com.sg/}{Informa
    Solutions}}{Singapore}{Software Engineer}{April 2017 - Dec. 2017}
  \begin{itemize}
    \item \resproject{MQB}{On assignment from Luxoft Vietnam, see above}
  \end{itemize}

  \newpage

\item \ressubheading{\href{https://www.fpt-software.com/}{FPT
    Software}}{Software Engineer}{Ho Chi Minh, Vietnam}{Nov. 2013 - Oct. 2015}
  \begin{itemize}
    \item \resproject{Video Input Processing}{Develop software to process RTP
      stream into segmented video stream}
         \begin{itemize}
           \item Used \cplusplus{}11 and boost to develop a system to process
             RTP stream which received from program provider (HBO, CNN,
             etc...) by blacking out, filtering advertisement scene (to
             replace it later), packetising, encrypting (with AES\Minus{}256),
             recording in real\Minus{}time to a format conformed with DASH
             and/or HLS standard.
           \item Technology: \cplusplus{}11, Boost, DASH, HLS, RHEL
         \end{itemize}
  \end{itemize}

\end{itemize}

\resheading{Other Development Experience}
\begin{itemize}
  \item Contributed minor improvement for git, dracut, notmuch, etc...
  \item Contributed to VoidLinux's build systems.
  \item Maintain some Void Linux's Packages.
\end{itemize}

\resheading{Education}
\begin{itemize}
  \item[]
    \ressubheading{FPT University}{Ho Chi Minh, Vietnam}{B.Eng. in Software
    Engineer}{Sept. 2013}
\end{itemize}
\end{document}
